\documentclass[11pt]{article}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage[margin=1in]{geometry}

\hypersetup{colorlinks=true,linkcolor=black,citecolor=blue,urlcolor=blue}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{definition}{Definition}
\newtheorem{remark}{Remark}
\newtheorem{proposition}[theorem]{Proposition}

\title{Hanzo AI Chain Soundness\\
{\large Attestation, Provenance, and Identity Binding for AIVM
Inference Receipts}}
\author{Hanzo AI\\
\texttt{research@hanzo.ai}}
\date{Spec freeze: 2026-04-15 \\ Effective: 2026-04-20}

\begin{document}
\maketitle

\begin{abstract}
The Hanzo AI Chain is the Lux A-Chain (AIVM) deployed under the Hanzo
brand. It records inference receipts, model-provenance commitments,
agent-identity bindings, and TEE attestation quotes. We prove
soundness of the AIVM cert pipeline by composition with QuasarCert
(Theorem 7.5 of \cite{quasar-cert}) and add four AI-specific lemmas:
(i)~model-hash binding, (ii)~agent-DID binding, (iii)~TEE attestation
chain integrity, (iv)~inference-receipt non-malleability.  We then
state and prove the soundness theorem of the Hanzo AI Chain cert
pipeline: an inference receipt finalised on the A-Chain commits to a
unique tuple
$(\mathsf{model\_hash}, \mathsf{agent\_did}, \mathsf{quote},
\mathsf{input\_hash}, \mathsf{output\_hash})$ that no PPT or QPT
adversary can substitute except with negligible probability.
\end{abstract}

\tableofcontents

%% ==================================================================
\section{Background}
\label{sec:bg}
%% ==================================================================

The Lux A-Chain is the AI / Attestation chain in the LP-134 chain
topology~\cite{lp134}. Its VM is named \emph{AIVM} (deliberately
distinct from upstream Avalanche's ``AVM''; see
\cite{taxonomy}). Hanzo runs the A-Chain under the Hanzo brand as the
\emph{Hanzo AI Chain}.

The A-Chain stores three classes of records:
\begin{enumerate}[nosep]
  \item \textbf{TEE attestation quotes} (LP-127), bound to a
        \texttt{quote\_root} on the A-Chain state;
  \item \textbf{AI model registry} (LP-130), bound to a
        \texttt{model\_root} via Merkle commitment;
  \item \textbf{Inference receipts} bound to both roots and to the
        agent identity via DID.
\end{enumerate}

%% ==================================================================
\section{Definitions}
\label{sec:def}
%% ==================================================================

\begin{definition}[A-Chain certificate subject]
\label{def:a-subj}
The Lux LP-105 certificate subject for the A-Chain is
\[
  \mathsf{subj}_A = \mathsf{chain\_id}\,\|\,\mathsf{epoch}\,\|\,
                    \mathsf{round}\,\|\,A,
\]
where $A = \texttt{achain\_state\_root}$ is the Merkle root of the
A-Chain key/value store (LP-105 Def.~6.1, restated in
\cite{quasar-cert} Def.~1).
\end{definition}

\begin{definition}[Inference receipt]
\label{def:receipt}
An \emph{inference receipt} on the Hanzo AI Chain is a tuple
\[
  R = (\mathsf{model\_hash},\;
       \mathsf{agent\_did},\;
       \mathsf{quote},\;
       \mathsf{input\_hash},\;
       \mathsf{output\_hash},\;
       \mathsf{ts})
\]
where:
\begin{itemize}[nosep]
  \item $\mathsf{model\_hash}$ is the SHA3-256 hash of the model
        weights file as registered in the A-Chain model registry;
  \item $\mathsf{agent\_did}$ is a DID of form \texttt{did:lux:agent:<id>};
  \item $\mathsf{quote}$ is a TEE attestation (Nitro Enclave, AMD
        SEV-SNP, or Intel TDX) over the model+inference workload;
  \item $\mathsf{input\_hash}, \mathsf{output\_hash}$ are SHA3-256
        commitments of the I/O.
\end{itemize}
The receipt is committed via Merkle inclusion in
$\texttt{achain\_state\_root}$ for some block $b$.
\end{definition}

\begin{definition}[AI threat model]
\label{def:adv}
Adversary $\mathcal{A}$ is a non-uniform PPT (or QPT) algorithm that
controls a Byzantine stake fraction $f < 1/3$ and additionally
controls an arbitrary subset of agent operators. $\mathcal{A}$ can
register fraudulent models, request inferences from honest agents,
and observe all on-chain state. $\mathcal{A}$ \emph{wins} if it
produces an A-Chain block with QuasarCert-verified
$\mathsf{subj}_A^\star$ that includes an inference receipt $R^\star$
attributing an inference to model $m$ when $m$ was not actually
executed under a valid TEE quote bound to $\mathsf{agent\_did}$.
\end{definition}

%% ==================================================================
\section{AI-specific lemmas}
\label{sec:lemmas}
%% ==================================================================

\begin{lemma}[Model-hash binding]
\label{lem:model-hash}
If the model registry contract (LP-130) is collision-resistant
(SHA3-256), and an inference receipt $R$ verifies on-chain, then
$R.\mathsf{model\_hash}$ is bound to exactly one registered model
entry.
\end{lemma}

\begin{proof}
The model registry stores a Merkle tree with leaves
$(\mathsf{model\_hash}, \mathsf{owner}, \mathsf{license})$. The root
is committed inside the A-Chain state root $A$, which is in turn
committed inside $\mathsf{subj}_A$ (Def.~\ref{def:a-subj}). Forging a
distinct registry entry for the same $\mathsf{model\_hash}$ requires a
SHA3-256 collision; this is bounded by
$2^{-128}$~\cite{nist-hash}. The receipt-to-registry binding is via
Merkle inclusion; opening to a wrong leaf requires forging a Merkle
path, also reduces to SHA3-256 collision resistance.
\end{proof}

\begin{lemma}[Agent-DID binding]
\label{lem:agent-did}
The DID document for $\mathsf{agent\_did}$ is published on the
A-Chain attestation registry and signed with the agent's identity
key under the triple-hybrid scheme of
\cite[Crypto/Hybrid.lean]{lux-lean} (Ed25519 + ML-DSA + SLH-DSA).
A receipt verifying with $\mathsf{agent\_did}$ implies the agent's
authorisation under all three schemes simultaneously.
\end{lemma}

\begin{proof}
Triple-hybrid identity sig requires forging \emph{all three}
schemes. By \cite[Theorem 1]{lux-lean-hybrid}, classical DL on
Curve25519, plus MLWE+MSIS for ML-DSA, plus hash-only assumptions
for SLH-DSA, are independent. Forging the hybrid reduces to
forging all three; advantage is bounded by the minimum of the
individual advantages, all negligible (one classical, two PQ).
\end{proof}

\begin{lemma}[TEE attestation chain integrity]
\label{lem:tee}
Let $\mathsf{quote}$ be a Nitro / SEV-SNP / TDX attestation chain
verified by the LP-127 attestation pre-compile. If the quote
verification accepts, then with overwhelming probability the
inference was executed inside a TEE matching the model hash and
public key bound by $\mathsf{quote}$.
\end{lemma}

\begin{proof}
Nitro Enclaves attestation is a Cose\_Sign1 over a PCR-bound document
signed by AWS root keys; SEV-SNP and TDX are equivalent in structure.
The LP-127 pre-compile verifies the signature chain to the vendor
root, which is registered in the A-Chain attestation root. Forging a
quote requires either (a) compromising the vendor root key, or (b)
violating the TEE boundary. Both are out of scope for the consensus
adversary by Def.~\ref{def:adv}; we assume them as standard. (See
\cite{lp127} for the formal vendor-root trust assumption.)
\end{proof}

\begin{lemma}[Inference-receipt non-malleability]
\label{lem:nonmall}
If $R = (\mathsf{model\_hash}, \mathsf{agent\_did}, \mathsf{quote},
\mathsf{input\_hash}, \mathsf{output\_hash}, \mathsf{ts})$ is finalised
in A-Chain block $b$, no adversary can produce a distinct
$R' \neq R$ that hashes to the same Merkle leaf.
\end{lemma}

\begin{proof}
The leaf is $\mathsf{SHA3\text{-}256}(R)$; collision resistance gives
the result.
\end{proof}

%% ==================================================================
\section{Hanzo AI Chain soundness theorem}
\label{sec:soundness}
%% ==================================================================

\begin{theorem}[Hanzo AI Chain cert pipeline soundness]
\label{thm:soundness}
Suppose
\begin{itemize}[nosep]
  \item the QuasarCert system is sound (Theorem 7.5 of
        \cite{quasar-cert});
  \item SHA3-256 is collision-resistant;
  \item the triple-hybrid identity sig is unforgeable
        (\cite{lux-lean-hybrid});
  \item the LP-127 attestation pre-compile faithfully implements its
        vendor root checks.
\end{itemize}
Then for every PPT (resp. QPT) adversary $\mathcal{A}$ as in
Def.~\ref{def:adv},
\[
  \Pr[\mathcal{A} \text{ wins}] \;\leq\;
  \mathsf{Adv}^{\mathrm{forge}}_{\mathrm{QuasarCert}} +
  \mathsf{Adv}^{\mathrm{coll}}_{\mathrm{SHA3}} +
  \mathsf{Adv}^{\mathrm{forge}}_{\mathrm{Hybrid}} +
  \mathsf{Adv}^{\mathrm{TEE}}.
\]
\end{theorem}

\begin{proof}
We compose Lemmas~\ref{lem:model-hash}--\ref{lem:nonmall}. Suppose
$\mathcal{A}$ wins by producing a fraudulent receipt $R^\star$
finalised in block $b^\star$. Two cases:

\paragraph{Case 1: $\mathsf{subj}_A^\star$ was not endorsed by an
honest quorum.}
Then $\mathcal{A}$ forged a QuasarCert; advantage at most
$\mathsf{Adv}^{\mathrm{forge}}_{\mathrm{QuasarCert}}$.

\paragraph{Case 2: $\mathsf{subj}_A^\star$ was endorsed.}
Then $R^\star$ is attested by 2/3 of stake. The receipt's
$\mathsf{agent\_did}$ binds via Lemma~\ref{lem:agent-did}; substituting
agent identity reduces to forging the triple-hybrid sig, advantage
$\mathsf{Adv}^{\mathrm{forge}}_{\mathrm{Hybrid}}$.
The receipt's $\mathsf{model\_hash}$ binds via
Lemma~\ref{lem:model-hash}, advantage
$\mathsf{Adv}^{\mathrm{coll}}_{\mathrm{SHA3}}$ to forge.
The receipt's $\mathsf{quote}$ binds via Lemma~\ref{lem:tee},
advantage $\mathsf{Adv}^{\mathrm{TEE}}$.
Lemma~\ref{lem:nonmall} rules out malleability.
By union bound, the total adversary advantage is the stated sum.
All four terms are negligible under the stated assumptions.
\end{proof}

\begin{corollary}[Receipt non-repudiation]
\label{cor:nonrep}
A finalised inference receipt cannot be repudiated by the agent
operator: the triple-hybrid sig binds the operator's keys to the
receipt content with overwhelming probability.
\end{corollary}

%% ==================================================================
\section{GPU residency for AIVM}
\label{sec:gpu}
%% ==================================================================

LP-137~\cite{lp137} mandates GPU-residency for high-throughput
verification. The A-Chain inherits this invariant directly: receipt
verification under Quasar 3.0 is offloaded to GPU validators when
LP-132's GPU adapter is enabled (\cite{lp132}). No additional proof
is needed in this paper; we cite the LP-132/137 GPU-residency lemmas
as a shared dependency.

\begin{remark}[Inference cost vs. settlement cost]
GPU-residency applies to consensus verification, not inference
itself. Inference is performed off-chain in TEE; only the
attestation quote and receipt are recorded.  The cost model
distinguishes \emph{compute} (off-chain, billed via Hanzo Commerce)
from \emph{settlement} (on-chain, billed via Lux gas + Liquidity
Protocol margin).
\end{remark}

%% ==================================================================
\section{Worked example: end-to-end inference}
\label{sec:example}
%% ==================================================================

Consider an inference call:
$\mathrm{user} \to \mathrm{Hanzo SDK} \to \mathrm{agent} \to
 \mathrm{TEE} \to \mathrm{output}$.

\begin{enumerate}[nosep]
  \item \textbf{Discovery.} The Hanzo SDK reads the A-Chain
        model registry, picks model $m$ with hash $h_m$ and the
        cheapest registered agent $a$ with attestation root in
        the recent A-Chain attestation tree.
  \item \textbf{Request.} The user's prompt is sent (encrypted to
        the agent's enclave key) to agent $a$.
  \item \textbf{TEE execution.} Agent $a$ executes inference inside
        Nitro/SEV-SNP/TDX. The TEE produces the output and a
        signed quote $\mathsf{quote}$ over the workload+pubkey.
  \item \textbf{Receipt.} Agent $a$ assembles
        $R = (h_m, \mathrm{did}_a, \mathsf{quote},
             H(\mathrm{prompt}), H(o), \mathsf{ts})$ and signs
        with its triple-hybrid identity key.
  \item \textbf{Submission.} Agent $a$ submits $R$ to the A-Chain
        block proposer; the block records $R$ inside
        $\texttt{achain\_state\_root}$.
  \item \textbf{Finality.} Block $b$ commits with QuasarCert
        $\mathcal{C}_b$.
\end{enumerate}

By Theorem~\ref{thm:soundness}, no party --- including the agent
operator --- can subsequently fabricate or alter the receipt; the
output is provably tied to the registered model and the agent's
DID.

%% ==================================================================
\section{Storage layout}
\label{sec:layout}
%% ==================================================================

\begin{table}[h]
\centering
\caption{A-Chain storage cells relevant to the receipt pipeline.}
\begin{tabular}{lll}
\toprule
Cell & Type & Size \\
\midrule
$\texttt{model\_root}$        & \texttt{bytes32} (Merkle)   & 32 B \\
$\texttt{quote\_root}$        & \texttt{bytes32} (Merkle)   & 32 B \\
$\texttt{agent\_root}$        & \texttt{bytes32} (Merkle)   & 32 B \\
$\texttt{receipt\_log}$       & growable list of $H(R)$     & 32 B per entry \\
$\texttt{achain\_state\_root}$ & root over above            & 32 B \\
\bottomrule
\end{tabular}
\end{table}

The QuasarCert subject $\mathsf{subj}_A$ commits to
$\texttt{achain\_state\_root}$, which inductively commits to the
four sub-roots above.

%% ==================================================================
\section{Detailed reduction: lemma \ref{lem:model-hash}}
\label{sec:reduct-model}
%% ==================================================================

We expand the proof of Lemma~\ref{lem:model-hash} into a concrete
hybrid argument.

\paragraph{Game $\mathsf{G}_0$.} The real game.  The adversary
$\mathcal{A}$ submits a receipt $R^\star$ and a Merkle path
$\pi^\star$ opening to a model registry leaf
$(\mathsf{model\_hash}^\star, \mathsf{owner}^\star,
  \mathsf{license}^\star)$ where the model registered for
$\mathsf{model\_hash}^\star$ has different
$(\mathsf{owner}, \mathsf{license})$ on the canonical chain.

\paragraph{Game $\mathsf{G}_1$.} Identical to $\mathsf{G}_0$ except
that the simulator extracts the colliding
$\mathsf{model\_hash}^\star$ from the path and outputs it as a
SHA3-256 collision claim.

\paragraph{Reduction.} A successful $\mathcal{A}$ in
$\mathsf{G}_0$ implies (a)~the chain's Merkle tree contains a leaf
with $\mathsf{model\_hash}^\star$ and the canonical
$(\mathsf{owner}, \mathsf{license})$, and (b)~$\mathcal{A}$ produced
a path opening to a leaf with the same
$\mathsf{model\_hash}^\star$ but different metadata. The two leaves
hash to the same Merkle node only if a SHA3-256 collision occurs at
some level. The simulator outputs the colliding pre-images.

\paragraph{Probability.} $\Pr[\mathcal{A}\text{ wins }\mathsf{G}_0]
\leq \Pr[\mathsf{coll}_{\mathrm{SHA3}}] \leq Q^2 / 2^{256}$ for $Q$
hash queries.  At $Q = 2^{60}$ (one quintillion queries),
$Q^2 / 2^{256} = 2^{120 - 256} = 2^{-136}$, vastly below the
$2^{-128}$ threshold.

%% ==================================================================
\section{Detailed reduction: lemma \ref{lem:agent-did}}
\label{sec:reduct-did}
%% ==================================================================

The triple-hybrid identity scheme $\Sigma_3 =
(\Sigma_{\mathrm{Ed25519}}, \Sigma_{\mathrm{ML\text{-}DSA}},
 \Sigma_{\mathrm{SLH\text{-}DSA}})$ accepts a triple
$(\sigma_1, \sigma_2, \sigma_3)$ iff all three component schemes
verify under the corresponding component public keys.

\paragraph{Adversary advantage decomposition.}
$\mathsf{Adv}^{\mathrm{forge}}_{\Sigma_3}(\mathcal{A}) =
 \Pr[\Sigma_3.\mathsf{Verify}(\mathsf{pk}, m, \sigma_1^\star,
                              \sigma_2^\star, \sigma_3^\star) = 1]$
where $m$ was never queried.  By definition of $\Sigma_3$ all three
component verifies pass; hence $\mathcal{A}$ produced forgeries for
\emph{each} of the three components on the same $m$.

\paragraph{Reduction to the minimum.}
A simpler bound: $\mathsf{Adv}^{\mathrm{forge}}_{\Sigma_3} \leq
\min(\mathsf{Adv}_{\mathrm{Ed25519}},
     \mathsf{Adv}_{\mathrm{ML\text{-}DSA}},
     \mathsf{Adv}_{\mathrm{SLH\text{-}DSA}})$. Reduction: an
$\mathcal{A}$ on $\Sigma_3$ produces, in particular, a forgery on
the Ed25519 component, hence reduces to Ed25519's classical
EU-CMA. Same argument for the PQ components.

The minimum of one classical-PQ-impossible (Ed25519, $2^{128}$
classical, broken by Shor) and two PQ-secure schemes is bounded
\emph{quantum-classically}: under a quantum adversary $\mathcal{A}_Q$,
$\mathsf{Adv}_{\mathrm{Ed25519}}^{\mathcal{A}_Q}$ is non-negligible
(Shor breaks classical signatures), but
$\mathsf{Adv}^{\mathrm{forge}}_{\Sigma_3,\mathcal{A}_Q}$ remains
$\leq \min(\mathsf{Adv}_{\mathrm{ML\text{-}DSA},\mathcal{A}_Q},
        \mathsf{Adv}_{\mathrm{SLH\text{-}DSA},\mathcal{A}_Q})
= \mathsf{negl}(\lambda)$ because all three components must verify
simultaneously.

\paragraph{Conclusion.} The triple-hybrid identity sig is
forwards-secure against quantum adversaries even though one of
its components (Ed25519) is not.

%% ==================================================================
\section{Cross-references with LPs}
\label{sec:lp-refs}
%% ==================================================================

\begin{itemize}[nosep]
  \item LP-105 -- QuasarCert spec (Def.~6.1, Theorems 7.5--7.8).
  \item LP-127 -- Attestation pre-compile.
  \item LP-130 -- AI model registry contract layer.
  \item LP-132 -- QuasarGPU verifier.
  \item LP-134 -- Chain topology (A-Chain definition).
  \item LP-137 -- GPU-residency invariant.
\end{itemize}

%% ==================================================================
\section{Composition with Liquidity Protocol}
\label{sec:lp-compose}
%% ==================================================================

The companion paper \cite{hanzo-adopts} adopts the Liquidity Protocol
on 2026-04-20 for inference-receipt settlement. The composition is
straightforward: an inference receipt that requires payment is
settled via an OMA swap on Lux C-Chain. Theorem~\ref{thm:soundness}
of this paper guarantees the receipt cannot be forged; the Liquidity
Protocol's atomicity (\cite{lp-paper} \S5) guarantees the payment is
either delivered or reverted; QuasarCert subject-binding
(\cite{quasar-cert} Theorem 7.8) prevents replay.

%% ==================================================================
\section{Status}
\label{sec:status}
%% ==================================================================

\begin{table}[h]
\centering
\caption{Hanzo AI Chain proof status, 2026-04-20}
\begin{tabular}{lll}
\toprule
Lemma / Theorem & Status & Evidence \\
\midrule
QuasarCert soundness         & Machine-checked (Lean) & \cite{quasar-cert} \\
Triple-hybrid sig            & Machine-checked (Lean) & Crypto/Hybrid.lean \\
Model-hash binding           & Paper proof (this work) & \S\ref{sec:lemmas} \\
Agent-DID binding            & Paper proof (this work) & \S\ref{sec:lemmas} \\
TEE attestation              & LP-127 + vendor roots   & \cite{lp127} \\
Receipt non-malleability     & Paper proof (this work) & \S\ref{sec:lemmas} \\
Hanzo AI Chain soundness     & Paper proof (this work) & \S\ref{sec:soundness} \\
\bottomrule
\end{tabular}
\end{table}

%% ==================================================================
\begin{thebibliography}{9}

\bibitem{quasar-cert}
Z.~Kelling.
\newblock QuasarCert Soundness: Canonical Formal Specification, Quasar 3.0.
\newblock \texttt{luxfi/proofs/quasar-cert-soundness.tex}, 2025-12-15.

\bibitem{taxonomy}
Lux Industries.
\newblock Lux Canonical Taxonomy.
\newblock \texttt{luxfi/lps/TAXONOMY.md}.

\bibitem{lp134}
Lux Industries.
\newblock LP-134 Lux Chain Topology.
\newblock \texttt{luxfi/lps/LP-134-lux-chain-topology.md}, 2025-12-15.

\bibitem{lp127}
Lux Industries.
\newblock LP-127 Attestation Pre-compile.
\newblock \texttt{luxfi/lps/LP-127-attestation.md}.

\bibitem{lp130}
Lux Industries.
\newblock LP-130 AI Model Registry.
\newblock \texttt{luxfi/lps/LP-130-ai.md}.

\bibitem{lp132}
Lux Industries.
\newblock LP-132 QuasarGPU Execution Adapter.
\newblock \texttt{luxfi/lps/LP-132-quasar-gpu-execution-adapter.md}.

\bibitem{lp137}
Lux Industries.
\newblock LP-137 GPU-Residency Invariant.
\newblock \texttt{luxfi/lps/LP-137-gpu-residency-invariant.md}.

\bibitem{lux-lean}
Lux Industries.
\newblock Lean 4 proof corpus.
\newblock \texttt{luxfi/proofs/lean/}.

\bibitem{lux-lean-hybrid}
Lux Industries.
\newblock Crypto/Hybrid.lean: triple-hybrid identity sig.
\newblock \texttt{luxfi/proofs/lean/Crypto/Hybrid.lean}.

\bibitem{nist-hash}
NIST.
\newblock FIPS 202: SHA-3 Standard.
\newblock 2015.

\bibitem{lp-paper}
Liquidity.io.
\newblock The Liquidity Protocol: Oracle-Mirrored AMM, v1.0.
\newblock \texttt{liquidityio/proofs/liquidity-protocol/}, April 2026.

\bibitem{hanzo-adopts}
Hanzo AI.
\newblock Hanzo Adopts the Liquidity Protocol.
\newblock \texttt{hanzoai/proofs/hanzo-adopts-liquidity-protocol.tex}, 2026-04-20.

\bibitem{hanzo-paper}
Hanzo AI.
\newblock Hanzo AI Chain (whitepaper).
\newblock \texttt{hanzoai/papers/hanzo-ai-chain/}.

\end{thebibliography}

\end{document}
